Tips for Writing a Research Paper using \LaTeX

### 2021-11-20 paper_writing_tips.tex
Fix minors
Update toc and tables

% For caption setup
\captionsetup[table]{aboveskip=3pt}
\captionsetup[table]{belowskip=2pt}
\captionsetup[figure]{aboveskip=5pt}
\captionsetup[figure]{belowskip=0pt}
\captionsetup{font=small}

@@

\author{Guanying Chen \\
{\tt\small \url{https://guanyingc.github.io}}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle
{
    \hypersetup{linkcolor=black}
    \tableofcontents
}

@@

%%%%%%%%% BODY TEXT
\vspace{6em}
\section{Introduction}
\label{sec:intro}
\LaTeX\ is a very powerful tool for documentation preparation, and is often used by researchers to prepare a manuscript for reviewing and publication. 
However, some new graduate students might not have experience in using \LaTeX and thus have a difficult time in prepare their first paper.

@@

\section{Tips for the Writing}
In this section, we provide some tips for paper writing. 
\begin{itemize}
    \item There should be a space before the open parentheses:\\
        \wrong{Convolutional neural network(CNN) has been successfully applied on various vision problems.}\\
        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
    \item There should be no space before the period and comma punctuation marks:\\
        \wrong{Convolutional neural network (CNN) has been successfully applied on various vision problems .}\\
        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
    \item There should be a punctuation at the end of the equation:
        \begin{align}
            \label{eq:eq1}
            & \textcolor{red}{E = mc^2 \quad \times} \\
            & \textcolor{blue}{E = mc^2. \quad \checkmark}
        \end{align}
    \item All equations should be numbered:
        \begin{align}
            \label{eq:eq2} \nonumber
            & \textcolor{red}{E = mc^2. \quad \times}\\ 
            & \textcolor{blue}{E = mc^2. \quad \checkmark}
        \end{align}
    \item The first character in a sentence should be capitalized:\\
        \wrong{how are you?}\\
        \correct{How are you?}
    \item Double quotation marks should be correctly typed:\\
        \wrong{Are you "okay"?}\\
        \correct{Are you ``okay''?}
    \item There should be a space before the citation:\\
        \wrong{A proposes a method B for this problem[1].}\\
        \correct{A proposes a method B for this problem~[1].}
    \item Do not include citations in the abstract.
    \item Use \textbackslash ie command for \ie and use \textbackslash eg for \eg.
    \item Define a macro for a word or phrase if it appears frequently (\eg, the method name and the dataset name). The command can be\\``\textbackslash newcommand\{\textbackslash NetName\}\{A Great Deep Net\}''.
    \item When referring to a table, also use ``Table~\ref{tab:table1}'' in a sentence.
    \item The table caption should be at the top of the table.
    \item When referring to a figure, use ``Figure~\ref{fig:figure1}'' at the beginning, and ``Fig.~\ref{fig:figure1}'' at the middle or the end of a sentence.
    \item The figure caption should be at the bottom of the table.
    \item It is better to put the tables and figures at the top of a page.
\end{itemize}

\clearpage
\section{Examples for the Tables}

% single column
\input{tables/table1} % simple table
\input{tables/table2} % multi-column table
\input{tables/table3} % multi-column with makecell
\input{tables/table4} % multi-column with vertical lines
\input{tables/table5} % multi-column with bold font
\newpage
\input{tables/table6} % multi-column with parallel lines
\input{tables/table_network2} % single-column network arch

@@

% two column
\input{tables/table8} % two-column table
\input{tables/table12} % two-column table with remarks
\input{tables/table9} % two-column table with color header
\input{tables/table7} % two-column table with two sub-tables
\input{tables/table_figure2} % two-column tables with images in the header
\input{tables/table10} % two tables side-by-side

\clearpage
\input{tables/table11} % table with caption at the left

\input{tables/table_network1} % two column network arch table

@@

\section{Examples for Figures}

% Single-column
\input{figures/figure1} % single image
\input{figures/figure2} % two images
\input{figures/figure3} % four images
\input{figures/figure4} % four images with text header
\input{figures/figure5} % four images with vertical text
\input{figures/figure6} % two sub figures
\input{figures/figure15} % figure numeric results and color bar

% Two column
\input{figures/figure7} % single image
\input{figures/figure8} % multiple images
\input{figures/figure9} % multiple images with two zoom in patches (horizontal)
\input{figures/figure11} % multiple images with two zoom in patches (vertical) 
\input{figures/figure13} % two figure placed side-by-side
\input{figures/figure12} % figure with caption at the left
\input{figures/figure14} % figure numeric results and color bar
\input{figures/figure10} % multiple images organized with multi-level

>>>>

% For caption setup
\captionsetup[table]{aboveskip=3pt}
\captionsetup[table]{belowskip=2pt}
\captionsetup[figure]{aboveskip=5pt}
\captionsetup[figure]{belowskip=0pt}
\captionsetup{font=normal}

@@

\author{Guanying Chen \\
{\tt\small \url{https://guanyingc.github.io}}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\onecolumn
\maketitle
{
    \hypersetup{linkcolor=black}
    \tableofcontents
}

@@

%%%%%%%%% BODY TEXT
%\newpage
\vspace{7em}

\section{Introduction}
\label{sec:intro}
\LaTeX\ is a very powerful tool for documentation preparation, and is often used by researchers to prepare a manuscript for reviewing and publication. 
However, some new graduate students might not have experience in using \LaTeX and thus have a difficult time in prepare their first paper.

@@

\twocolumn

\section{Tips for the Writing}
In this section, we point out some common mistakes in paper writing and give some suggestions for editing \LaTeX\ files.

\subsection{Some Common Mistakes}
\begin{itemize}
    \item There should be a space before the open parentheses:\\
        \wrong{Convolutional neural network(CNN) has been successfully applied on various vision problems.}\\
        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
    \item There should be no space before the period and comma punctuation marks:\\
        \wrong{Convolutional neural network (CNN) has been successfully applied on various vision problems .}\\
        \correct{Convolutional neural network (CNN) has been successfully applied on various vision problems.}
    \item There should be a punctuation at the end of the equation:
        \begin{align}
            \label{eq:eq1}
            & \textcolor{red}{E = mc^2 \quad \times} \\
            & \textcolor{blue}{E = mc^2. \quad \checkmark}
        \end{align}
    \item All equations should be numbered:
        \begin{align}
            \label{eq:eq2} \nonumber
            & \textcolor{red}{E = mc^2. \quad \times}\\ 
            & \textcolor{blue}{E = mc^2. \quad \checkmark}
        \end{align}
    \item The first character in a sentence should be capitalized:\\
        \wrong{how are you?}\\
        \correct{How are you?}
    \item Double quotation marks should be correctly typed:\\
        \wrong{Are you "okay"?}\\
        \correct{Are you ``okay''?}
    \item There should be a space before the citation:\\
        \wrong{A proposes a method B for this problem[1].}\\
        \correct{A proposes a method B for this problem~[1].}
\end{itemize}

\subsection{Some Suggestions}
\begin{itemize}
    \item Do not include citations in the abstract.
    \item Define a macro for a word or phrase if it appears frequently (\eg, the method name and the dataset name). The command can be\\``\textbackslash newcommand\{\textbackslash NetName\}\{A Great Deep Net\}''.
    \item Use ``\textbackslash ie'' command for ``\ie'' and use ``\textbackslash eg'' for ``\eg.''.
    \item When referring to a table, always use ``Table~\ref{tab:table1}'' in the sentence:\\
        \wrong{Our results are shown in Tab.~1.}\\
        \correct{Our results are shown in Table~1.}

    \item The table caption should be at the top of the table.
    \item When referring to a figure, use ``Figure~\ref{fig:figure1}'' at the beginning of a sentence and ``Fig.~\ref{fig:figure1}'' elsewhere.\\
        \wrong{Fig.1 shows our results.}\\
        \correct{Our results are shown in Fig.~1.}\\
        \correct{Figure~1 shows our results.}
    \item The figure caption should be at the bottom of the table.
    \item It is better to put the tables and figures at the top of a page.
\end{itemize}

\clearpage

\section{Examples for the Tables}

%\subsection{Examples for the Single-column Tables}
\input{tables/table1} % simple table
\input{tables/table2} % multi-column table
\input{tables/table3} % multi-column with makecell
\input{tables/table4} % multi-column with vertical lines
\input{tables/table5} % multi-column with bold font
\input{tables/table6} % multi-column with parallel lines
\input{tables/table_network2} % single-column network arch

@@

%\subsection{Examples for the Two-column Tables}
\input{tables/table8} % two-column table
\input{tables/table12} % two-column table with remarks
\input{tables/table9} % two-column table with color header
\input{tables/table7} % two-column table with two sub-tables
\input{tables/table13} % two-column table with cmidrule
\input{tables/table_figure2} % two-column tables with images in the header
\input{tables/table10} % two tables side-by-side
\input{tables/table11} % table with caption at the left
\input{tables/table_network1} % two column network arch table

@@

\section{Examples for the Figures}
%\subsection{Examples for the Single-column Figures}
\input{figures/figure1} % single image
\input{figures/figure2} % two images
\input{figures/figure3} % four images
\input{figures/figure4} % four images with text header
\input{figures/figure5} % four images with vertical text
\input{figures/figure6} % two sub figures
\input{figures/figure15} % figure numeric results and color bar

%\subsection{Examples for the Two-column Figures}
\input{figures/figure7} % single image
\input{figures/figure8} % multiple images
\input{figures/figure9} % multiple images with two zoom in patches (horizontal)
\input{figures/figure11} % multiple images with two zoom in patches (vertical) 
\input{figures/figure13} % two figure placed side-by-side
\input{figures/figure12} % figure with caption at the left
\input{figures/figure14} % figure numeric results and color bar
\input{figures/figure10} % multiple images organized with multi-level
